### 2014-03-07 src/analysis.Rnw
update

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
@
\end{comment}

% <<a,message=F, echo=F>>=
% require(xtable)
% require(data.table)
% load('data/mu.rda')
% @

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

@@

<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@

>>>>

\section{Analysis}
\label{sec:analysis}
\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

@@

### 2014-03-07 src/paper.Rnw
update

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

o <- subset(oprand, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(oprand, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
@

<<results='asis'>>=
opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))

o <- subset(opsel, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(opsel, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE)
@

\subsection{Correlation Analysis}

$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $

The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.

\subsubsection{sdl.mut.avg and mut.avg}

% <<>>=
% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
% @

$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$

\subsubsection{lrnd.mut.avg and mut.avg}

$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$

\subsection{Regression Analysis}
The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling. We can perform two statistical tests to answer this question. For the first, we run a simple paired t-test.

%<<>>=
%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
%@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
Our full model is

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
% <<results='asis'>>=
% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
% s$type <- 'sdl'
% colnames(s) <- c('mut', 'sample', 'type')
% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
% r$type <- 'rnd'
% colnames(r) <- c('mut', 'sample', 'type')
% all <- rbind(s, r)
% fm <- with(all, lm(mut ~ sample + type + sample:type))
% sm <- anova(fm)
% print(xtable(sm,caption="My caption"), size="\\small")
% @
\end{small}

We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness. Hence, the techniques random sampling and statement deletion operator do not have any difference.

\begin{figure*}[t]
% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% t_f <- sdl.time~lrnd.time
% plot(t_f, main='SDL ~ RND',pch='*')
% abline(lm(t_f), col='red')
% detach(m)
% @
\caption{Time}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/original.pdf}
\caption{Subsumption Original}
\label{fig:subsumptiono}
\end{figure*}[t]

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]

<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@

>>>>

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@
